Students' Alcohol Consumption impacts on academic Results on the example of a secondary Scool Maths Class in Portugal

### 2016-10-12 MSproject.Rmd

## Students' Alcohol Consumption impacts on academic Results on the example of a secondary Scool Maths Class in Portugal

@@

```{r pressure, echo=FALSE}
sm <- read.csv("student-mat.csv", sep=';')

summary(sm[,"age"])
```

The data set examined provides sample data of two secondary schools in Portugal. The ages of students varies from 15 to 22 years with an average of 16.7 years.

@@

## Appendices

@@

# Attributes in the Dataset: 
1 school - student's school (binary: 'GP' - Gabriel Pereira or 'MS' - Mousinho da Silveira)

>>>>

# Students' Alcohol Consumption impacts on academic Results on the example of a secondary Scool Maths Class in Portugal

@@

```{r pressure, echo=FALSE}
sm <- read.csv("student-mat.csv", sep=';')
str(sm)
summary(sm[,"age"])
```

The dataset examined provides sample data of two secondary schools in Portugal, providing a total of 395 objects (students) and 33 variables (items on information on each student). The data could be split into six areas of information:

### 1. Generic Information
2. Family  
3. Education
4. Social life  
5. Health 
6. Grades
The data is includes an abbreviation for each school, sex of the students The ages of students varies from 15 to 22 years with an average of 16.7 years.

Alongside generic information on each student

@@

# Appendices

@@

## Attributes in the Dataset: 
1 school - student's school (binary: 'GP' - Gabriel Pereira or 'MS' - Mousinho da Silveira)
